Schema Change: Challenge Problems

### 2024-05-02 paper.tex
comment
We could expand the scope to include conventional DBs, asking for a more declarative solution than hand-coded SQL.

~
\textcolor{red}{[JE] We could expand our context to include conventional DB systems not just live/local. It is a widespread problem, attested by the many tools to assiste with it. We could include in our problems a description of a typical solution with a standard DB as a sort of baseline. }

>>>>

~
\textcolor{red}{[JE] We could expand our context to include schema change for conventional DB systems, not just live/local. It is a widespread problem, attested by the many tools that assist with it, but all of them come down to manually coding SQL. We could call for a higher-level declarative solution. }
